---
title: "Example"
author:
  name: "Quinn Asena"
  affiliation: "UW-Madison (Formaly University of Auckland)"
date: today
format:
  html:
    code-fold: true
    toc: true
    link-external-newwindow: true
theme:
  light: flatly
  dark: darkly
---

# Introduction

This template is designed to accompany the slide deck and to include most of the features you will need to use for hosting a collaborative research project. I've included a few extras that I find handy (e.g., YAML entries, and check out the plot loop!). Every research project needs to be taylored towards your collaborators, data, data privacy, and the list goes on.

Some things are the same across projects like well commented code and a well documented version control history. I use documents like this (previously in Rmarkdown) to share results easily with a link hosted on GitHub. Replace this blurb with a summary of your project and any useful links, references and content you desire.

## A note on project structure

Today, we have cloned an existing project structure. It is important that you create a project structure that works for your particular case. A general framework is to create a primary directory that is your repo and contains your `.qmd` script, and sub directories for data, outputs.

- /primary_directory

  - script.qmd

  - .git, .gitignore

  - /data

    - data.csv

  - /outputs

    - results

Plenty of tools exist for reproducibility (such as the `renv` package to record package versions used in your project).

# Packages and libraries {.unlisted}

It is good practice to include a list of packages used as well as and source files or functions up front. `{.unlisted}` will exclude the section from the table of contents. You can hide the section completely with `{.unlisted .hidden}`. This is useful for sections like packages which are included for reproducibility and are necessary to execute as code but maybe unnecessary to display. If your sections are numbered (insert `number-sections: true` in [YAML](https://quarto.org/docs/output-formats/html-basics.html#section-numbering)) then you will need `{.unlisted. unnumbered .hidden}` to hide the section.

I also include individual functions or sourcing scripts of functions in this section.

```{r Libraries}
#| include: true

# install.packages("pacman") # Install pacman package
library(pacman) # Load pacman package
pacman::p_load(ggplot2, patchwork, palmerpenguins)    # Install & load packages
```

# You can't see me! {.unlisted .hidden}

Lah lah lah!

I'm here in spirit, code will still be executed.

# Data wrangling

Typically you need to do some tidying of your data. Each project will have different reqirements e.g., transforming data or generating new datasets. You probably want to dedicate a section just for wrangling but may want to hide it from the output. See [R for Data Science](https://r4ds.had.co.nz/introduction.html) for more info.


# Visualisations {.tabset}

Sometimes I have a lot of plots (like, a lot!). Perhaps generated from a loop that outputs a list of related plots. It is possible to programatically generate panel tabsets rather that repeatedly writing out the heading `#` and inserting the plot (e.g., `plot_list[[1]]`). As an example, I've grabbed a couple of plots from [Alison Horst](https://allisonhorst.github.io/palmerpenguins/articles/examples.html) again.

```{r}
# Two plots:
flipper_hist <- ggplot(data = penguins, aes(x = flipper_length_mm)) +
  geom_histogram(aes(fill = species), alpha = 0.5, position = "identity") +
  scale_fill_manual(values = c("darkorange","purple","cyan4")) +
  labs(x = "Flipper length (mm)",
       y = "Frequency",
       title = "Penguin flipper lengths")

flipper_box <- ggplot(data = penguins, aes(x = species, y = flipper_length_mm)) +
  geom_boxplot(aes(color = species), width = 0.3, show.legend = FALSE) +
  geom_jitter(aes(color = species), alpha = 0.5, show.legend = FALSE, position = position_jitter(width = 0.2, seed = 0)) +
  scale_color_manual(values = c("darkorange","purple","cyan4")) +
  labs(x = "Species",
       y = "Flipper length (mm)")

# Stick them in a list:
plot_list <- list(Histogram = flipper_hist, Box = flipper_box)

# Make some heading names:
headings <- names(plot_list)
```

## Plot tabs

The code might be a little complicated but useful to reduce the length and manual work if you have a lot of outputs.

::: {.panel-tabset}
```{r, results='asis', echo = FALSE}
#| warning: false

# Use a loop (or lapply, or map, you choose) to generate the headings and insert plots
for (i in seq_along(plot_list)) {
  cat("# ",headings[i],"\n")
  print(plot_list[[i]])
  cat('\n\n')
}
```
:::

# References

References will appear here!