---
title: "Your awesome project title"
author:
  name: "You et al"
  affiliation: "From whence you hail"
date: today
bibliography: refs.bib
format:
  html:
    code-fold: false
    link-external-newwindow: true
theme:
  light: flatly
  dark: darkly
---

:::{.callout-tip}
# YAML exersice
- Fill the `title: ` and `name: ` and `affiliation: ` fieds.

  - a couple of handy entries are already completed

  - the existing field: `date: today` will automatically generate today's date (cool huh?  ͡▀̿ ̿ ͜ʖ ͡▀̿ ̿ )

- Add a table of contents following the [guide](https://quarto.org/docs/output-formats/html-basics.html)

- Remove this callout block and render the document

- Give me a :heavy_check_mark: when done or a :hand: if you need help
:::

# Introduction

:::{.callout-tip}
# Markdown exercise

- Check out [Quarto's markdown guide](https://quarto.org/docs/authoring/markdown-basics.html)

- and the [biostats guide to writing](https://biostats-r.github.io/biostats/quarto/04-figures-tables.html#equations)

In the template Introduction section take 3-4 minutes to write:

- a sub-heading under the introduction

- a list

- and an equation

- cite one of the articles in in existing `.bib` file using the `@`

- remove this callout  and render the document and hit the :heavy_check_mark: in zoom
:::

# Libraries {.unnumbered .unlisted}

Generally it is good practice to include a list of packages you use up front. But you may not need to show them in the output or list them in the table of contents. The `{.unnumbered .unlisted}` commands following the title remove this section from the table of contents but it will remain in the text. Quarto accepts multiple coding languages, the following example uses R. I have set up working R code chunks so that for this tutorial you do not need to be familiar with R necessarily. The code block options **May be the same...**
If you want to use Python code check out the documentation [here](https://quarto.org/docs/computations/python.html#overview).


:::{.callout-tip}
# Code block exercise

- Check out the [Block options](https://quarto.org/docs/computations/execution-options.html) and edit the existing code block options below to:

 - exclude the results, messages and warnings

 - exclude the code from the HTML output

 - render the document and hit the :heavy_check_mark: in zoom
:::


```{r Libraries}
#| include: true

# install.packages("pacman") # Install pacman package
library(pacman) # Load pacman package
pacman::p_load(ggplot2, patchwork, palmerpenguins)    # Install & load packages
```

# 

# Plots  {.tabset}
```{r}
library(ggplot2)
library(patchwork)
gg0 <- list()

p1 <- ggplot(mtcars, aes(mpg, hp)) + geom_point()
p2 <- ggplot(mtcars, aes(mpg, disp)) + geom_point()
p3 <- ggplot(mtcars, aes(mpg, drat)) + geom_point()

gg0[[1]] <- p1/p1/p1/p1
gg0[[2]] <- p1/p1/p1/p1/p1/p1
gg0[[3]] <- p1/p1/p1/p1/p1/p1/p1/p1/p1

headings <- c('hp','disp','drat')
```

#### Heading

::: {.panel-tabset}
```{r, results='asis', echo = FALSE}
for (i in 1:length(gg0)) {
  cat("##### ",headings[i],"\n")
  print(gg0[[i]])
  cat('\n\n')
}
```

:::

# References