---
title: "Example"
author:
  name: "Quinn Asena"
  affiliation: "UW-Madison (Formaly University of Auckland)"
date: today
format:
  html:
    code-fold: true
    toc: true
    link-external-newwindow: true
theme:
  light: flatly
  dark: darkly
---

# Introduction

This template is designed to include most of the features you will need to use for publishing a collaborative research project. I've included a few extras that I find handy (e.g., YAML entries, and check out the plot loop!). Every research project needs to be taylored towards your collaborators, data, data privacy, and the list goes on.

Some things are the same across projects like well commented code and a well documented version control history. I use documents like this (previously in Rmarkdown) to share results easily with a link hosted on GitHub. Replace this blurb with a summary of your project and any useful links, references and content you desire.

# Packages and libraries {.unnumbered .unnumbered}

It is good practice to include a list of packages used as well as and source files or functions up front. `{.unnumbered .unnumbered}` will exclude the section from the table of contents.

# Plots  {.tabset}
```{r}
library(ggplot2)
library(patchwork)
gg0 <- list()

p1 <- ggplot(mtcars, aes(mpg, hp)) + geom_point()
p2 <- ggplot(mtcars, aes(mpg, disp)) + geom_point()
p3 <- ggplot(mtcars, aes(mpg, drat)) + geom_point()

gg0[[1]] <- p1/p1/p1/p1
gg0[[2]] <- p1/p1/p1/p1/p1/p1
gg0[[3]] <- p1/p1/p1/p1/p1/p1/p1/p1/p1

headings <- c('hp','disp','drat')
```

#### Heading

::: {.panel-tabset}
```{r, results='asis', echo = FALSE}
for (i in 1:length(gg0)) {
  cat("##### ",headings[i],"\n")
  print(gg0[[i]])
  cat('\n\n')
}
```

:::