---
title: "Authoring collaborative research projects using Quarto"
author: "Quinn Asena"
institute: "UW-Madison"
date: today
bibliography: refs.bib
format:
  revealjs:
    backgroundcolor: "#44444c"
    fontcolor: "white"
    preview-links: true
#    incremental: true  
    highlight-style: github
    slide-number: c/t
    width: 1600
    height: 900
---

# Nothing to see here
```{r}
#| echo: false
options(tidyverse.quiet=TRUE)
library(tidyverse)
```

# Quarto {background-color="#44444c"}

# Quarto {background-color="#36365a"}


## Quarto

Why geek out on Quarto?

[This is why](linktoresource)

## Quarto

- [Well documented](https://quarto.org/docs/guide/)

- Uses [markdown syntax](https://quarto.org/docs/authoring/markdown-basics.html)

- Accepts multiple programming languages

- Outputs multiple formats (Word, PDF HTML...)


## Elements of a Quarto file

::: {.incremental}
- YAML
- Text
- Code blocks
- Citation .bib
- css (optional for style)
:::


## YAML

:::: {.columns}
::: {.column width="50%"}
The YAML is a set of `key: value pairs` that are the metadata for your document. such as, author, title, output format, css and citation file.

- YAML is whitespace sensitive

- tab sensitive?

:::

::: {.column width="50%"}
``` yaml
---
title: "My Manuscript"
format: html
date: today
---
```
:::
::::

## YAML

::: callout-tip
# YAML Exersice
- Open up the template.qmd and fill the existing YAML fields

- Add a table of contents following the [guide](https://quarto.org/docs/output-formats/html-basics.html)
:::


## Text

- Writing in Quarto uses markdown syntax. 

- LaTeX is used to render PDFs so LaTeX commands can be used for PDF outputs

- Why I like writing in Markdown

Look! I can do fancy maths: $f_{c}=z^{2}+c$

## Code blocks

## Citations

@perkel2022


## A slide with a plot {.scrollable}

```{r}
#| echo: true
#| fig.retina: 2
#| fig.height: 9
#| fig.width: 16
#| output-location: column
# ^^ could be fragment, slide, column, column-fragment
ggplot() +
  geom_point(
    data = mtcars,
    aes(wt, mpg),
    color = "goldenrod"
  ) +
  labs(
    title = "Some Dots"
  ) 
```

## Python

```{.python code-line-numbers="6-8"}
import numpy as np
import matplotlib.pyplot as plt

r = np.arange(0, 2, 0.01)
theta = 2 * np.pi * r
fig, ax = plt.subplots(subplot_kw={'projection': 'polar'})
ax.plot(theta, r)
ax.set_rticks([0.5, 1, 1.5, 2])
ax.grid(True)
plt.show()
```

## References